Emissions and Perceptions of Climate Change

### 2022-11-30 Code/Drafts/Final_Short_Oral_Presentation.Rmd
changing headers

---
title: "Emissions and Perceptions of Climate Change"
author: "Rae Dunbar"
date: "11/13/2022"
output:
  pdf_document: default
  html_document: default
---

## Introduction

@@

## Preparing R
```{r, message=FALSE}
rm(list=ls())
library(tidyverse)
library(here)
library(ggfortify)
library(forecast)
library(gridExtra)
```

## Statistcal Analysis and Results

@@

### Climate Change Emissions of Countries

@@

#### Creating the figure

@@

#### What about the Rate of Decrease?

@@

#### Running the Test
Lets run a paired t test

@@

### Perceptions of Climate Change

@@

### More or less Fossil Fuels

@@

#### Running the Statistical Test

@@

## Summary & Discussion

@@

## Limitations
The data used is from a survey conducted on Facebook, so all respondents are Facebook users. This adds a confounding variable, when utilizing this study.

## Challenges

>>>>

---
title: "Emissions and Perceptions of Climate Change"
author: "Rae Dunbar"
date: "11/13/2022"
output:
  html_document: default
  pdf_document: default
---

# Introduction

@@

# Preparing R
```{r, message=FALSE}
rm(list=ls())
library(tidyverse)
library(here)
library(ggfortify)
library(forecast)
library(gridExtra)
```

# Statistcal Analysis and Results

@@

## Climate Change Emissions of Countries

@@

### Creating the figure

@@

### What about the Rate of Decrease?

@@

### Running the Test
Lets run a paired t test

@@

## Perceptions of Climate Change

@@

## More or less Fossil Fuels

@@

### Running the Statistical Test

@@

# Summary & Discussion

@@

# Limitations
The data used is from a survey conducted on Facebook, so all respondents are Facebook users. This adds a confounding variable, when utilizing this study.

# Challenges
